Slides for Social Network Paper

### 2025-03-11 ProjectBlog/paper2/Paper 2 Slides 2/p2literature.qmd
paper 2 update
p2 updates

>>>>

# Outline for Social Network Paper

<iframe src="pdfs/2_27_Paper_2_Outline.pdf" style="width:100%; height:1500px;" frameborder="0">

Conference: https://2025.cswimworkshop.org/

# Mechanism Paper

<iframe src="pdfs/send-down.pdf" style="width:100%; height:1500px;" frameborder="0">

# Causal Inference Methods

<iframe src="pdfs/Machine learning in causal inference for epidemiology.pdf" style="width:100%; height:1500px;" frameborder="0">
